---
title: "HW5"
author: "Ben Lehmnn"
date: "2023-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
https://github.com/BenLehmann12/Chocolate

#Question Set 1
```{r}
library(ggplot2)

#1852

choc <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")

ggplot(choc, aes(x=Rating)) + geom_histogram() + facet_wrap(~Review.Date)
```


Question Set 2
```{r}
ggplot(choc, aes(x=Rating)) + geom_histogram()

#We see an outlier with the rating near 5, we also see a skew in the distribution

print(cor(choc$Cocoa.Pct,choc$Rating))   #-0.16  (Not much correlation, so, no)

filter(choc, Company.Location %in% c("U.S.A.", "France", "Canada"))

```

```{r}
x_c = choc[choc$Company.Location %in% c("U.S.A.", "France", "Canada"),]

ggplot(x_c, aes(x=Rating)) + geom_bar() + facet_wrap(~Company.Location)

```


In year 2017, which companies produced the best chocolate(Mean rating per company)
```{r}
choc_2017 = choc[choc$Review.Date == 2017,]
best = aggregate(Rating ~ Company, choc_2017, FUN=mean)
ggplot(best, aes(x=Rating,y=reorder(Company,Rating))) + geom_col()
```
Zotter(Austria),Coppeneur(Germany), 

Conclusion: I noticed, I took a look at the top 10, and what I noticed is that the top chocolate comes from
Europe, however, we did have one company from the US


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
